\documentclass[10pt]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{url}

\parindent 0cm

\begin{document}

\onecolumn

\pagestyle{empty}
\begin{center}
{\bfseries \Huge Chairs' Welcome}
\end{center}

\bigskip
\bigskip

%\large

It is our great pleasure to welcome you to FARM 2016, the 4th ACM
SIGPLAN International Workshop on Functional Art, Music, Modelling and
Design!

\medskip

The ACM SIGPLAN International Workshop on Functional Art, Music,
Modelling and Design (FARM) gathers together people who are harnessing
functional techniques in the pursuit of creativity and expression.

\medskip

Functional Programming has emerged as a mainstream software
development paradigm, and its artistic and creative use is booming. A
growing number of software toolkits, frameworks and environments for
art, music and design now employ functional programming languages and
techniques. FARM is a forum for exploration and critical evaluation of
these developments, for example to consider potential benefits of
greater consistency, tersity, and closer mapping to a problem domain.

\medskip

By gathering researchers, practitioners, artists, designers and anyone
interested, FARM aims to develop this interdisciplinary field. Work in
this challenging area has already led to new language designs,
abstraction techniques, and execution models, as well as the use of
old ideas in new, novel, and surprising ways.

\medskip

After its first edition held in Boston in 2013, its second edition held in
Gothenburg in 2014, the third in Vancouver 2015, this year's FARM will
take place in Nara, Japan on September 24.

\medskip

FARM 2016 is once again dominated by contributions on computer
music: Jay McCarthy's paper shows how do construct computer music with
classic 80's style 8-bit synthesis as found on the Nintendo
Entertainment System.  Chris Ford demonstrates the Klangmeister
livecoding environment for music composition and synthesizer
construction, and also presents a call for collaboration on
algomusicology.  Jean Bresson, John MacCallum and Adrian Freed
describe the o.OM system for structuring the communication between
computer music systems.  Dave Yarwood presents the Alda
music-composition language.

\medskip

However, music is not all there is to be had at FARM: David Janin and
Simon Archipoff give deep insights into the algebraic structure of
reactive polymorphic media.  Caleb Helbling and Samuel Guyer present
the Juniper language for functional-reactive programming on the
Arduino.  Jakob Leben presents the Arrp language for describing
multi-dimensional signals.  Csongor Kiss and Toby Shaw present the
VoxelCAD tool for constructing 3D shapes.  Tom Murphy extends
functional-reactive programming by livecoding elements.  Finally,
Francis Shuman will show us hypnotic images generated by simulating
video feedback.

\medskip

In 2014 and 2015, FARM also organized an evening of performances on
the last day of ICFP.  This year continues what is becoming a
tradition, with a line-up of exciting computer-music performances
assembled by Renick Bell.

\medskip

Further information about FARM is available on our website,
\url{functional-art.org}.

\medskip

We would like to thank ACM and the organizers of ICFP 2016 for their
support, especially chairs Jacques Garrique and Gabriele Keller as
well as the workshop chairs, Nicolas Wuh and Andres Löh. Thanks also
to the members of the FARM Program Committee, and to everyone who
submitted papers, demos, and performance proposals. And, of course, we
are grateful to all of the participants. We hope that you will enjoy
the workshop as much as we know we will.

\medskip

\medskip

Welcome to the FARM!

\bigskip





\hskip -.25cm 
\begin{tabular}[t]{l}
{\bf David Janin}\\
Workshop Chair\\
University of Bordeaux
\end{tabular}
\hfill
\begin{tabular}[t]{l}
 {\bf Michael Sperber}\\
Program Committee Chair\\
Active Group GmbH
\end{tabular}
\hfill
\begin{tabular}[t]{l}
{\bf Renick Bell}\\
Performance Chair\\
\end{tabular}
\hfill
\begin{tabular}[t]{l}
  {\bf Mark Santolucito}\\
  Publicity Chair\\
  Yale University
\end{tabular}

\vspace{2mm}

\newpage
\begin{center}
{\bfseries \Huge FARM 2016 Workshop Organization}
\end{center}

\bigskip

\large
\begin{center}
\begin{tabular}{rl}

{\bf Workshop Chair:} & David Janin (\emph{University of Bordeaux})\\
\\

{\bf Workshop Chair:} & Michael Sperber (\emph{Active Group GmbH})\\
  \\

  {\bf Performance Chair:} & Renick Bell\\
  \\

{\bf Publicity Chair:} & Mark Santolucito (\emph{Yale University})\\

\\

  {\bf Program Committee:} & Renick Bell\\
                      & Rebecca Fiebrink (\emph{Goldsmiths University of London})\\
                      & David Janin (\emph{University of Bordeaux})\\
                      & Akihiro Kubota (\emph{Tama Art University)}\\
                      & John Lato (\emph{Google})\\
                      & José Pedro Magalhães (\textit{Standard Chartered Bank} and \textit{Chordify})\\
                      & Alex McLean (\emph{University of Leeds})\\
                      & Dan Piponi (\emph{Google})\\
                      & Prabhakar Ragde (\emph{University of Waterloo})\\
                      & Mark Santolucito (\emph{Yale})\\
                      & Fabienne Serrière (\emph{KnitYak})\\
                      & Michael Sperber (\emph{Active Group GmbH})\\
                      & John Stell (\emph{University of Leeds})
\end{tabular}
\end{center}

\vspace{2mm}

\end{document}
